Template for indicator documentation

### 2023-09-14 slitasje.Rmd
#104

```{r dense-stats, fig.height= 12, fig.cap="Barplot showing the number of data points, the area weighted indicator values and the sd for the slitasje indicator. Transparrent bars represents categories with less than 150 data points."}
temp_plot <- all_stats %>%
  mutate(HIF_NA = case_when(
    n > 150 ~ HIF
  ))

@@

ggarrange(
ggplot(temp_plot, aes(x = region, y = n, group = HIF, fill = HIF_NA))+
  geom_bar(position = "dodge", stat = "identity", col="black")+
  theme_bw(base_size = 10)+
  scale_fill_brewer(palette="Oranges")+
  theme(axis.text.x = element_text(angle = 90, vjust=0.5))+
  coord_flip()+
  facet_wrap(.~eco),
ggplot(temp_plot, aes(x = region, y = w_mean, group = HIF, fill = HIF_NA))+
  geom_bar(position = "dodge", stat = "identity", col="black")+
  theme_bw(base_size = 10)+
  scale_fill_brewer(palette="Oranges")+
  theme(axis.text.x = element_text(angle = 90, vjust=0.5))+
  coord_flip()+
  facet_wrap(.~eco),
ggplot(temp_plot, aes(x = region, y = sd, group = HIF, fill = HIF_NA))+
  geom_bar(position = "dodge", stat = "identity", col="black")+
  theme_bw(base_size = 10)+
  scale_fill_brewer(palette="Oranges")+
  theme(axis.text.x = element_text(angle = 90, vjust=0.5))+
  coord_flip()+
  facet_wrap(.~eco),
ncol = 1)

>>>>

```{r dense-stats, fig.height= 12, fig.cap="Barplot showing the number of data points, the area weighted indicator values and the sd for the ADSV indicator. Transparent bars represents categories with less than 150 data points."}
temp_plot <- all_stats %>%
  mutate(HIF_NA = case_when(
    n > 150 ~ HIF
  ))

@@

ggarrange(
ggplot(temp_plot, aes(x = region, y = n, group = HIF, fill = HIF_NA))+
  geom_bar(position = "dodge", stat = "identity", col="black")+
  theme_bw(base_size = 10)+
  scale_fill_brewer(palette="Oranges", na.translate=F)+
  theme(axis.text.x = element_text(angle = 90, vjust=0.5))+
  coord_flip()+
  labs(fill = "HIF")+
  facet_wrap(.~eco),
ggplot(temp_plot, aes(x = region, y = w_mean, group = HIF, fill = HIF_NA))+
  geom_bar(position = "dodge", stat = "identity", col="black")+
  theme_bw(base_size = 10)+
  scale_fill_brewer(palette="Oranges",  na.translate=F)+
  theme(axis.text.x = element_text(angle = 90, vjust=0.5))+
  coord_flip()+
  labs(fill = "HIF")+
  facet_wrap(.~eco),
ggplot(temp_plot, aes(x = region, y = sd, group = HIF, fill = HIF_NA))+
  geom_bar(position = "dodge", stat = "identity", col="black")+
  theme_bw(base_size = 10)+
  scale_fill_brewer(palette="Oranges",  na.translate=F)+
  theme(axis.text.x = element_text(angle = 90, vjust=0.5))+
  coord_flip()+
  labs(fill = "HIF")+
  facet_wrap(.~eco),
ncol = 1)
